\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\input{structure.tex} % Include the file specifying the document structure and custom commands

\begin{document}

\head
  % {http://tomasortega.com/}
  {}
  {Tomás Ortega Rojas}
  % {tomasvortegargmail.com}  % Personal Email
  {tor213@nyu.edu}  % NYU Email
  {+1 (305) 988-7211}
  {https://github.com/tomasort}
  {tomasort}
  {https://www.linkedin.com/in/tomas-ortega}
  {tomas-ortega}

%   SUMMARY   %
% \section{Summary}
% \sectionStart
%   \summaryText
%   {Senior Computer Science student with experience in developing full stack web applications using technologies such as JavaScript (ES6), ExpressJS and MongoDB. Seeking a \textbf{Summer 2018 Internship} to leverage exemplary coding skills, analytical skills and leadership skills.}
% \sectionEnd

%   EDUCATION   %
\section{Education}
\sectionStart
% NYU
  \educationItem
    {New York University}
    {Graduate School of Arts and Science, New York, NY} 
    {May 2022}
    {Master of Science} 
    {Computer and Information Sciences} 
    {3.88/4.0}
    {
      % Computer Vision, 
      Big Data Science, 
      % Compiler Construction (Java), 
      Deep Learning Systems, 
      % DevOps and Agile Methodologies,
      % Computer Graphics (C++), 
      Artificial Intelligence
      % Practical Computer Security
      }

% FIU 
  \educationItem
    {Florida International University}
    {School of Computing and Information Sciences, Miami, FL} 
    {May 2019}
    {Bachelor of Science} 
    {Computer Science} 
    {3.84/4.0}
    {
      % Data Structures and algorithms (Java), 
      % Computer Networking (Python), 
      Databases, 
      % Computer Systems (C and Unix), 
      Graph Theory, 
      % Algorithm Techniques and Design, 
      % Game Theory, 
      % Software Engineering
      Linear Algebra
    }
\sectionEnd

%   SKILLS   %
\section{Technical Skills}
\sectionStart

  % Programming Languages
  \skillItem
    {Programming Languages}
    {Proficient in Java, Python, C/C++, JavaScript and SQL |
      Familiar with Matlab and PHP}

  % Frameworks
  \skillItem
    {Libraries and Frameworks}
    {Flask, 
      Pandas, 
      Numpy,
      Matplotlib, 
      Pytorch, 
      Keras, 
      Plotly, 
      ScikitLearn, 
      Hadoop, 
      Spark}

  % Software
  \skillItem
    {Tools}
    {Bash, 
      Git, 
      VirtualBox, 
      Docker, 
      PostgreSQL, 
      MongoDB, 
      Amazon AWS, 
      \LaTeX\ }
  \vspace{3pt}
\sectionEnd

%   PROJECTS   %
\section{Projects}
\sectionStart

  % % Self Driving Car
  % \projectHeading
  %   {https://github.com/tomasort/SelfDrivingCar}
  %   {Self-Driving Car}
  %   {(JavaScript, HTML, CSS)}
  %   {May 2022 - Present}
  %   % Description
  %   {something}
  % % What did you do?
  % \listStart
  %   \bulletItem
  %     {Developed a car racing game that allows the user to control a car through different real world scenarios.}
  %   \bulletItem
  %     {Implemented a neural network using JavaScript and trained it using a genetic algorithm for driving through a street while avoiding obstacles.}
  % \listEnd

  \projectHeading
    {https://github.com/tomasort/TextureSynthesis}
    {Texture Synthesis GAN}
    {(Python, PyTorch, Jupyter Notebooks)}
    {Sep 2021 - Dec 2021}
    % Description
    {Generative Adversarial Network (GAN), trained to generate different regular textures that can be used in 3D models.}
  % What did you do?
  \listStart
    \bulletItem
      {Improved the performance of the original model to achieve better textures by using data augmentation }
  \listEnd


  \projectHeading
    {https://github.com/tomasort/RayTracer}
    {Ray Tracer}
    {(C++, Eigen)}
    {Aug 2021 - Dec 2021}
    % Description
    {Application for rendering 3D meshes and primitive objects such as spheres and rectangles using ray tracing}
  % What did you do?
  \listStart
    \bulletItem
      {Implemented the ray tracing algorithm from scratch using c++ and Eigen (library for linear algebra).}
    \bulletItem
      {Applied an optimization algorithm called AABB Trees to accelerate the rendering of 3D triangle meshes. This dramatically improved the rendering speed for large 3D meshes }
  \listEnd

  \projectHeading
    {https://github.com/tomasort/PhishingWebsiteDetection}
    {Phishing Website Detection}
    {(Python, Scikit-Learn, Web Crawling)}
    {Jan 2021 - June 2021}
    % Description
    {Command Line Application that determines if a website is malicious or not using machine learning.}
  % What did you do?
  \listStart
    \bulletItem
      {Created a web crawler using python to extract information from a collection of 100,000 websites. }
    \bulletItem
      {Trained machine learning algorithms for classifying websites as malicious or legitimate, achieving an accuracy of 95\%}
  \listEnd

  % Data Science Workflow Manager
  \projectHeading
    {https://github.com/fiu-airlab/Data-Science-Workflow-Manager}
    {Data Science Workflow Manager}
    {(Python, Plotly, Flask)}
    {Jan 2019 - May 2019}
    % Description
    {Web application for building and automating data science pipelines.}
  % What did you do?
  \listStart
    \bulletItem
      {Designed and Implemented the UX/UI using HTML, CSS and, JS along Plotly for data visualizations. }
    \bulletItem
      {Collaborated with a team of graduate students and developed tools to automate data cleaning, passing data to models and visualizing the results.}
  \listEnd

  \projectHeading
    {https://github.com/tomasort/GeekText}
    {GeekText}
    {(ReactJS, JavaScript, Flask)}
    {January 2017 - April 2017}
    % Description
    {Web application where users can browse, and purchase books.}
  % What did you do?
  \listStart
    \bulletItem
      {Developed an API using python and Flask to process the product information and get data from the database. }
    \bulletItem
      {Created a React component for displaying information about a selected book along with its rating, and comments. }
    \bulletItem
      {Collaborated in a team of 5 and applied software engineering principles along with the scrum agile methodology to complete the project. }
  \listEnd

  % \projectHeading
  %   {https://github.com/tomasort/BaconNumberGenerator}
  %   {Bacon Number Calculator}
  %   {(Java)}
  %   {Jan 2017 - April 2017}
  %   % Description
  %   {Command line application that gets the bacon number (number of vertices needed to link two actors).}
  % % What did you do?
  % \listStart
  %   \bulletItem
  %     {Developed graph algorithms to efficiently find the distance between any two actors in the IMDB database. }
  % \listEnd

\sectionEnd
  
%   EXPERIENCE   %
\section{Experience}
\sectionStart

  \jobHeading
    {Freelancing \& Volunteering}
    {Jun 2020 - Present}
    {New York City, New York, NY}
  \listStart
    \bulletItem
    {Worked directly with clients documenting requirements, and developing websites for e-commerce and blogging.}
  \listEnd

  \jobHeading
    {Web Developer Intern}
    {Aug 2019 - Jun 2020}
    {GBP Solutions, Miami, FL}
  \listStart
    \bulletItem
    {Implemented web scrapers using Python, BeautifulSoup and Selenium to get real estate data from multiple sources.}
    \bulletItem
    {Worked on a web application using Python, Flask, and PostgreSQL for statistical analysis of real state data.}
    \bulletItem
    {Developed application to find properties with similar characteristics in a specific geographic location within a specified radius using PostGIS.}
  \listEnd

  \jobHeading
    {Programming I and II Tutor}
    {Aug 2018 - Dec 2018}
    {Florida International University, Miami, FL}
  \listStart
    \bulletItem
    {Analyzed and debugged code with students to provide feedback.}
    \bulletItem
    {Applied strong communication skills and problem-solving techniques working with students through programming exercises.}
  \listEnd

\sectionEnd

% %   LEADERSHIP   %
% \section{Leadership}
% \sectionStart
%   \jobHeading
%     {Student Facilitator}
%     {February 2017 - Present}
%     {ASU Student and Cultural Engagement [Tempe, AZ]}
%   \listStart
%     \bulletItem
%     {Facilitated diversity \& inclusion workshops for 80 students on topics such as conflict resolution, cultural adjustment and intersectionality of sex, gender \& sexuality.}
%   \listEnd
%   \jobHeading
%     {Vice President}
%     {September 2017 - April 2018}
%     {ASU Coalition of International Students [Tempe, AZ]}
%   \listStart
%     \bulletItem
%     {Coordinated 58 student leaders within the coalition to host 5 large-scale events that celebrated culture from all around the world that collectively engaged over 6,000 students throughout the academic year.}
%     \bulletItem
%     {Supervised all internal operations within the coalition such as project management and conducting strategic reviews.}
%   \listEnd
% \sectionEnd

\end{document}